Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-06 ipsj/paper.tex
Add system model

%2
\section{System Model}

\subsection{TECS}
TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

@@

\subsubsection{開発フロー}

@@

>>>>

%2
\section{System Model}
\label{sec:System Model}

This section describes the system model of the proposed framework, including basic technologies such as TECS.
The system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mrubyonTECS}) are described.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

\subsection{mruby}
\label{sec:mruby}

\subsection{TECS}
\label{sec:TECS}

TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

@@

\subsubsection{Development Flow}

@@

\subsection{mruby on TECS}
\label{sec:mrubyonTECS}
